
\chapter{Components}
\label{chap:components}

This appendix contains list of all important\footnote{Components for debugging are omitted.} components with their comprehensive description.
In order to save space in the printed version of the thesis the list of interfaces is available only int the web user interface.

All components are in the main project called \emph{Malsys} int the namespace \emph{Malsys.Processing.Components}.
If some component is in sub-namespace, then the path from the main namespace is in the bracket after component type.

All listed components can be accessed in process configurations by type name or full name (type name with all namespaces).
For example component called \nameref{Malsys.Processing.Components.Interpreters.TurtleInterpreter} can be accessed by name \texttt{TurtleInterpreter} or full name \texttt{Malsys.Processing.Components.Interpreters.TurtleInterpreter}.

\section{Legend}

Explanation of tags which describes special properties of some members.

\begin{description*}
	\item[abstract]
		Components marked as \emph{abstract} can not be instantiated.
		They can be used in the same way as interfaces (only as container type).
	\item[run-time only]
		Gettable properties (or callable functions) marked as \emph{run-time only} can be get (called) only while L-system is processed (in rewrite rules or interpretation methods).
		Especially they can not be get (called) in L-system let or set statements.
	\item[mandatory]
		Value of settable properties (and settable symbol properties) marked as \emph{mandatory} must be set in L-system definition.
		Parameters of interpretation method marked as \emph{mandatory} must be supplied to interpretation method.
	\item[optional]
		Connectable properties marked as \emph{optional} may not be connected by process configuration (by default they must be connected).
	\item[allowed multiple]
		More components can be connected to connectable properties marked as \emph{allowed multiple} (by default only one component can be connected).
		
\end{description*}


\input{apx-components-generated}

